### 2019-04-02 papers/journal/intro.tex
Moved the discussion about the size of the system upfront

\subsubsection{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\subsubsection{Vesicle fusion involves two steps} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.

@@

%\somya{schematic of snare regulatory network}
\subsubsection{Schematic of snare regulatory network}
In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
%
Whereas, SM proteins have following multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

%\somya{schematic of intracellular compartments and  major routes}
\subsubsection{Major paths in the vesicle transport network}
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}. 
%
%\begin{table}
%	\begin{center}
%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%			\hline
%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
%			\hline
%		\end{tabular}
%		\label{tab:threec}
%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
%	\end{center}	
%\end{table}

\subsection{The model}
The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed.
\item Each compartment is in steady state, gain and loss of the molecules is balance.
\item Molecules are neither created nor destroyed.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
\item An active SNARE pair is necessary and sufficient for fusion. 
\end{enumerate}
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

\subsubsection{The cell as a transport graph} 
%We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph. Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.
The cell can be abstractly represented as an annotated graph. 
Every compartment in the cell can be represented as a node in the graph. 
%
The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
%
The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
%This represents the flux of the molecule type present at that compartment.
%
The transport vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
% 
The label represents the associated flux of all molecular types carried by the corresponding vesicle.
%
%

\subsubsection{Steady state} 
The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
%
In our model, we assume that the cell is in steady state. As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment. 
Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
%
In this paper, we refer to the steady state of the cell (referred to as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.

@@

\subsubsection{Vesicle fusion}
%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
%
%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
% 
%The molecular composition and hence the properties of the transfer vesicle 
%is the crucial factor to which target compartment the vesicle will fuse to.
%
%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%  
%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
%
%Once a vesicle has budded out of the source, the molecules it carries determine its properties. In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment. Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment. 
%
%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
Vesicle fusion requires a pairing of 3 Qsnares and 1 Rsnare that are distributed between the transfer vesicle and the target compartment. 
%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%
%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
%
Not all sets of Q and R SNAREs are allowed to fuse with each other.
%
In the model, we assume that the cell has an equal number of Q and R SNARE types.
%
Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
% equal number of Q and R SNAREs as a part of node and edge label.
%
%
Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.

\subsubsection{Molecular regulation} 
Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
%We assume that for fusion to occur, the pair of 
%
The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
%
In our abstract model, 
we create a hierarchy of models for varying degrees of regulation of SNARE activity.
%we create a set of variations of different kind of molecular regulations.
%
Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
%
We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
%
This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
%

>>>>

\textbf{Vesicle budding} involves sorting and packaging of cargo molecules, membrane deformation and budding of the vesicle from the source compartment~\ref{fig:vts}.
%
Cargo sorting is performed by cytosolic adaptor proteins. 
Adaptors are recruited to the source compartment through interactions with the lipids that form the compartment's membrane, and interactions with molecular switches called Arf/Sar which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}. 
%
Then these adaptors bind to cargo molecules and thereby sequester them for packaging. 
%
Different adaptor proteins act at different compartments, for example, vesicle formation at the ER requires the adaptor sec23/24, and the AP2 adaptor is used for packaging vesicles at the plasma membrane.
%

@@

\textbf{Vesicle fusion involves two steps:} recognition of the correct target compartment and fusion of the transport vesicle~\ref{fig:vts}.

@@

%\somya{schematic of snare regulatory network}
\textbf{Schematic of snare regulatory network:}
In keeping with their central role in vesicle transport, both the activity and the localization of SNARE proteins are regulated. Notable regulators are Sec17/18 and the SM proteins.
%
Sec17/18 bring about disassembly of SNARE complexes post-fusion in order that these SNAREs may be reused. 
%
Whereas, SM proteins have following multiple modes of SNARE regulation: 
\begin{itemize}
	\item SM proteins can hold
	the Qa-SNAREs in an inhibited state and prevent or postpone their assembly into SNARE
	complexes.
	%
	\item Some SM proteins can act as a template upon which an early SNARE complex intermediate can
	form.
	%
	\item Finally, SM proteins bind the fully assembled
	SNARE complexes to protect them from premature disassembly by Sec17/18~\cite{baker2016chaperoning}.
	%
	\item SM proteins have also been shown to interact with tethers~\cite{yoon2018snare}.
\end{itemize}

%\somya{schematic of intracellular compartments and  major routes}
\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major routes of vesicle transport in all eukaryotic cells.
%
\begin{itemize}
	\item The secretory route takes proteins from the ER (their site of production) to the plasma membrane( from where they are secreted out of the cell) via the Golgi apparatus\cite{alberts2002molecular}.
	%
	\item The endocytic route takes proteins from the outside of the cell, through the plasma membrane, to the endocytic compartments and the lysosome where they are digested. 
\end{itemize}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent back and forth between the Trans-Golgi network (secretory route) to the early and the late endosomes(endocytic route)\cite{progida2016bidirectional}. Also, recently, unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi apparatus. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}.

%

%\begin{table}
%	\begin{center}
%		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
%			\hline
%			Nodes & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
%			Graphs & 0 & 0 & 0 & 1 & 2 & 15 & 121 & 2159 & 68715 & 3952378 \\ 
%			\hline
%		\end{tabular}
%		\label{tab:threec}
%		\caption{Number of simple 3-edge-connected unlabelled N-node graphs.}
%	\end{center}	
%\end{table}

\subsection{The model}
\todo{Ankit: The Rothman model has no intuition; Add couple of lines relating it to VTS; Also, relate it to previous subsection. The connect is lacking.} The VTS model for this paper is inspired by~\cite{shukla2017discovering}. 
%
On the timescales of minutes, we have tried to capture important aspect of Rothman-Schekman-Sudhof (RSS) model~\cite{rothman2002machinery} of vesicle traffic system.
%
The following are the basic component and assumptions of our model. 
\begin{enumerate}
\item A cell is a set of compartments exchanging vesicles.
\item Compartments are neither created nor destroyed.
\item Each compartment is in steady state, gain and loss of the molecules is balance\todo{Ankit: Need intuition and also reasoning why this is okay to add this as an assumption}.
\item Molecules are neither created nor destroyed.
\item Molecules move via vesicles of uniform size.
\item Identical vesicles have identical target compartments.
\item Fusion of vesicles to compartments is driven by specific SNARE pairing.
%\item The identities of compartments and vesicles is encoded in their molecules, and identical vesicles fuse with identical target compartments.
\item The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.
\item An active SNARE pair is necessary and sufficient for fusion. 
\end{enumerate}

\todo{Ankit: Need some additional discussion;4 lines max about the legitamecy of the assumptions.}
%On the timescale of minutes, compartments are neither created nor destroyed, rather, they are in steady state. We assume that molecules are also neither created nor destroyed.
%The activity of a SNARE can be regulated by other molecules present on the same compartment or vesicle.

@@

\textbf{The cell as a transport graph:} 
%We consider a cell to be a collection of compartments (nodes) and vesicles (edges), thus defining a transport graph. Every compartment or vesicle has a set of molecular labels, such as SNARE proteins, associated with it.
The cell can be abstractly represented as an annotated graph. 
Every compartment in the cell can be represented as a node in the graph. 
%
The set of molecules present in the compartment, for example, SNARE proteins associated with it, are represented as a label to the corresponding nodes.
%
The label of each node will be unique molecules present on the compartment, i.e we abstract over the quantity of the molecule present in a compartment.
%This represents the flux of the molecule type present at that compartment.
%
The transport vesicle flowing from source compartment to the target compartment is represented by a labeled directed edge. 
% 
The label represents the associated flux of all molecular types carried by the corresponding vesicle.
%
%

\textbf{Steady state:} 
The vesicle transfer will change the molecular composition (distinct molecule count) on both the source compartment and the target compartment. 
%
In our model, we assume that the cell is in steady state. As a further simplification, we also assume that the incoming and outgoing flux is balanced for each of the molecular types at each compartment. 
Indeed, it is well accepted that on the scale of minutes and hours the molecular composition remains the same. 
%
In this paper, we refer to the steady state of the cell (referred to as \textit{homeostasis} in biological literature) as the stability condition over the annotated graph.

@@

\textbf{Vesicle fusion:}
%Based on the earlier discussion of fusion, the vesicle targeting is driven by molecular interactions.  
%
%Particularly, molecules composition (SNARE proteins etc) present on the budded vesicle determines it's properties, which 
% 
%The molecular composition and hence the properties of the transfer vesicle 
%is the crucial factor to which target compartment the vesicle will fuse to.
%
%For any given pair of a vesicle and a compartment, the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%  
%Biophysically, fusion of a vesicle to the target compartment requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment.
%
%Once a vesicle has budded out of the source, the molecules it carries determine its properties. In particular, for any given pair of a vesicle and a compartment, the set of SNARE proteins that label the former and latter influence whether the vesicle will fuse to that compartment. Biophysically, fusion requires a direct physical interaction between at least one SNARE type on the vesicle and one SNARE type on the compartment. 
%
%SNAREs are of two types (known as Q and R in the cell biology iterature) and 
Vesicle fusion requires a pairing of 3 Qsnares and 1 Rsnare that are distributed between the transfer vesicle and the target compartment. 
%For any given pair of a vesicle and a compartment, vesicle fusion requires a pairing of a Q-SNARE with an R-SNARE on 
%the SNARE proteins present on both influence the fusion of the vesicle to that compartment.
%
%The list of molecular pairs that can drive a fusion event is given in a pairing matrix between Q and R SNAREs. 
%
Not all sets of Q and R SNAREs are allowed to fuse with each other.
%
In the model, we assume that the cell has an equal number of Q and R SNARE types.
%
Therefore, we can abstract the underlying cell biology by labeling the nodes and edges with an equal number of Q and R SNAREs. 
% equal number of Q and R SNAREs as a part of node and edge label.
%
%
Given a relation of all allowed fusion SNARE pairings, we can computationally determine whether a particular transfer vesicle will fuse to a particular target compartment (the edge between two compartments) based on the above condition.

\textbf{Molecular regulation:} 
Fusion takes place only if the SNARE types involved in the vesicle and compartment are both in an active state.
%We assume that for fusion to occur, the pair of 
%
The activity of these SNAREs is dependent on the presence of other molecules on the vesicle or compartment, respectively.
%
In our abstract model, 
we create a hierarchy of models for varying degrees of regulation of SNARE activity.
%we create a set of variations of different kind of molecular regulations.
%
Most generally, the activity state of a given SNARE can be a Boolean function of all the molecular types on a compartment or vesicle. 
%
We have also tested \cite{shukla} a particularly simple regulation mechanism in which two SNAREs that can pair to drive fusion to inhibit one another; this is the \textit{pairing inhibition}. 
%
This is motivated by the idea that pairing must generate an inactive bi-molecular complex.
%
